Relative parabolic factorizations of Chevalley groups

### 2015-09-04 paper.tex
Finished rewriting Dennis---Vaserstein decomposition
Added Matsumoto lemma

%TODO: Rewrite this using better terminology.
For a representation $\pi$ of $\G(\Phi, R)$ on $V$ we denote by $\Lambda=\Lambda(\pi)$ the set of weights of $\pi$ and by $V_\lambda$ the weight subspace corresponding to $\lambda\in\Lambda$.
For any of the representations described above (with the sole exception of $(\rE_8, \varpi_8)$) all weight subspaces $V_\lambda$ are one-dimensional. 
This allows us to choose a basis $E_\pi=\{e_\lambda\}_{\lambda\in\Lambda}$.

@@

>>>>

For a representation $\pi$ of $\G(\Phi, R)$ on $V$ we denote by $\Lambda=\Lambda(\pi)$ the set of weights of $\pi$ and by $V_\lambda$ the weight subspace corresponding to $\lambda\in\Lambda$.

\textbf{TODO: Give definitions of $\Lambda^*$, $V^0$, the notion of ``basic representation''. }

For any of the representations described above (with the sole exception of $(\rE_8, \varpi_8)$) all weight subspaces $V_\lambda$ are one-dimensional. 
This allows us to choose a basis $E_\pi=\{e_\lambda\}_{\lambda\in\Lambda}$.

@@

The following result of H.~Matsumoto describes the action of elementary root unipotents in a basic representation of $\G(\Phi, R)$.
\begin{lemma}[{\cite[Lemma~2.3]{Ma69}}]\label{lemma:Matsumoto}
 Let $(V, \pi)$ be a basic representation of $\G(\Phi, R)$.
 One can choose a basis $v_\lambda$, $\lambda\in\Lambda(\pi)$ of $V$ such that the action of elementary root unipotents $t_\alpha(\xi)$ on it is described by the following formulae:
 \begin{thmlist}
  \item $t_{\alpha}(\xi) v_\lambda = v_\lambda$ for $\lambda\in\Lambda^*(\pi), \lambda+\alpha\not\in\Lambda(\pi)$;
  \item $t_\alpha(\xi)v_\lambda=v_\lambda\pm\xi v_{\lambda+\alpha}$ for $\lambda,\lambda+\alpha\in\Lambda^*(\pi)$;
  \item $t_\alpha(\xi)v_0 = v_0$ for every $v_0\in V^0$, $\alpha\not\in\Lambda^*(\pi)$;
  \item $t_\alpha(\xi)v_{-\alpha}=v_{-\alpha}\pm\xi v_0(\alpha)\pm\xi^2 v_{\alpha},$ $t_\alpha(\xi)v_0 = v_0\pm\xi\alpha_*(v_0)v_\alpha$ for $\alpha\in\Lambda^*(\pi)$.
 \end{thmlist}
\end{lemma}
